Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as show in Figure~\ref{Soot_pattern}.  From the photograph the areas of penetration and consumption can be clearly delininated while the discolored and sooted areas tend to meld together.  Further the focus of the measurements in this study are thermal, therefore the focus is on the burned, not burned line of demarcation.

>>>>

Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as show in Figure~\ref{Soot_pattern}.  From the photograph the areas of penetration and consumption can be clearly delineated while the discolored and sooted areas tend to meld together.  Further the focus of the measurements in this study are thermal, therefore the focus is on the burned, not burned line of demarcation.

\begin{figure}[p]
	\centering
	\includegraphics[width=2.5in]{../Figures/Soot_pattern}
	\includegraphics[width=2.5in]{../Figures/Soot_close}	\\
	\caption[Photographs showing clear lines of demarcation with gasoline]{Photographs showing clear lines of demarcation from a fire pattern generated on painted gypsum wallboard by a gasoline fueled burner.  Burned vs unburned area is clearly defined, where as the difference between sooted and thermally discolored areas is not as clear.}
	\label{Soot_pattern}
\end{figure}
